Usability of Modern Display Technologies

### 2014-10-21 mental-model-paper/paper2.tex
general structure complete

Touch screen interfaces have been popular for over 20 years, and concerns about touch screen accessibility have remained active throughout this time. \cite{Buxton:1986:HID:22339.22386} Previous research has explored techniques that make touch screens more accessible by modifying the hardware. This paper mentioned one such technique when explaining physical overlays.\cite{El-Glaly:2013:TTF:2460625.2460665} However, a recent study articulated how hardware modifications ``may be expensive to install, may limit the flexibility of the underlying software (by imposing physical structures), and may interfere with use by sighted people." \cite{Kane:2011:AOI:2047196.2047232}  The study asserts that for these reasons, techniques that rely upon hardware modifications have not been widely adopted.

\clearpage
More recent efforts have focused on using gestures to provide IBSVI with access to touch screens without modifying the underlying hardware. For example, Slide Rule \cite{Kane:2008:SRM:1414471.1414487} used multi-touch gestures to allow blind users to browse and explore content on a touch screen-based smartphone.

@@

@@

There exist several input entry methods, however, that attempt to address this problem. For instance, Tinwala and MacKenzie present a system that includes auditory and tactile feedback to guide eyes-free entry using speech and non-speech sounds. \cite{Tinwala:2010:ETE:1868914.1868972} 
Another proposed solution comes from Tactus Technology, a company in Fremont, California. Employees from Tactus Technology are creating a keyboard with shape-shifting keys that pop up from the screen's surface when needed and recede again when no longer necessary.\cite{Tactus} Craig Ciesla, the co-founder of the company, said that the keyboard will be offered later this year.

@@

\section{Discussion}
The principle of feedback
feedback ---sending back to the user information about what action has actually been done, what result has been accomplished--- is a well-known concept in the science of control and information theory\cite{Norman02} "In the good old days of the telephone", "telephones were designed with much more care and concern for the user. Designers at the Bell Telephone Laboratories worried a lot about feedback. The push buttons were designed to give an appropriate feel---tactile feedback. When a button was pushed, a tone was fed back into the earpiece so the user could tell that the button had been properly pushed. When the phone call was being connected, clicks, tones, and other noises gave the user feedback about the progress of the call." ``All this changed." ``Why are modern telephone systems so difficult to use? Basically, the problem is that the systems have more features and less feedback"

>>>>

\subsection{Prevailing Set of Views}
Most research pertaining to this limitation focuses on how the lack of tactile feedback affects the usability of the device for Individuals with Blindness or Severe Visual Impairment. Touch screen interfaces have been popular for over 20 years, and concerns about touch screen accessibility for IBSVI have remained active throughout this time. \cite{Buxton:1986:HID:22339.22386} The prevailing set of views on the subject recognize that the touch screens are not effective for the IBSVI, and propose solutions specifically to address needs of the IBSVI.

Previous research has explored techniques that make touch screens more accessible by modifying the hardware. This paper mentioned one such technique when explaining physical overlays.\cite{El-Glaly:2013:TTF:2460625.2460665} However, a recent study articulated how hardware modifications ``may be expensive to install, may limit the flexibility of the underlying software (by imposing physical structures), and may interfere with use by sighted people." \cite{Kane:2011:AOI:2047196.2047232}  The study asserts that for these reasons, techniques that rely upon hardware modifications have not been widely adopted.

More recent efforts have focused on using gestures to provide IBSVI with access to touch screens without modifying the underlying hardware. For example, Slide Rule \cite{Kane:2008:SRM:1414471.1414487} used multi-touch gestures to allow blind users to browse and explore content on a touch screen-based smartphone.

@@

There exist several input entry methods, however, that attempt to address this problem. For instance, Tinwala and MacKenzie present a system that includes auditory and tactile feedback to guide eyes-free entry using speech and non-speech sounds. \cite{Tinwala:2010:ETE:1868914.1868972}

@@

\clearpage
\subsection{Emerging technology}
There is technology emerging that is not necessarily aimed to specifically help the IBSVI.

Another proposed solution comes from Tactus Technology, a company in Fremont, California. Employees from Tactus Technology are creating a keyboard with shape-shifting keys that pop up from the screen's surface when needed and recede again when no longer necessary.\cite{Tactus} Craig Ciesla, the co-founder of the company, said that the keyboard will be offered later this year.

@@

\section{Discussion}
Research discusses usability for IBSVI but does has not delved into technology that can be effective for the sighted and IBSVI alike.
The principle of feedback
feedback ---sending back to the user information about what action has actually been done, what result has been accomplished--- is a well-known concept in the science of control and information theory\cite{Norman02} "In the good old days of the telephone", "telephones were designed with much more care and concern for the user. Designers at the Bell Telephone Laboratories worried a lot about feedback. The push buttons were designed to give an appropriate feel---tactile feedback. When a button was pushed, a tone was fed back into the earpiece so the user could tell that the button had been properly pushed. When the phone call was being connected, clicks, tones, and other noises gave the user feedback about the progress of the call." ``All this changed." ``Why are modern telephone systems so difficult to use? Basically, the problem is that the systems have more features and less feedback"
